Stack Safety as a Security Property

### 2020-06-10 main.tex
Notes on things to write about
Add Well-bracketed control flow

>>>>

\section{Well Bracketed Control Flow}

  Our integrity and confidentiality properties concern themselves with data,
  and may hold on a wide range of programs that violate expected control flow.
  But some forms of security rely on protected control flow. In a classic
  example, a system call that launches a missile might be gated behind code
  that checks a password. A piece of malicious code might jump into the middle
  of the sequence and execute the system call without the appropriate password,
  and still obey integrity if the malicious code never returns to its caller.
  Even with basic control flow protections, a return oriented programming
  attack could overwrite the return address to produce the same effect.

  Well bracketed control flow prevents this style of attack by guaranteeing
  that every jump between functions is either a call or a return, and each
  return jumps to the instruction after a corresponding call.

  \paragraph*{Separating Code}

    We extend our model with an explicit notion of functions and their code.
    Each function has an identifier, and the partial function \(\mathit{own}\)
    maps an address to the function in which it is an instruction.
    %
    \[\funid \in \FUNIDS\]
    %
    \[\own:\WORDS \rightharpoonup \FUNIDS\]

  \paragraph*{Return Maps}

    A {\em return map} is analogous to a call map, abstracting the recognition
    of a state representing the end of a return sequence. In this case
    \(\retmap \in \RETMAPS\) is a predicate on machine states.

  \definition{Control Separation}

    A system enjoys {\em control separation} with regard to an ownership
    function \(\own\), a call map \(\callmap\), and a return map \(\retmap\)
    if for any initial state \(\mach_0\) and any adjacent pair of states
    \(\mach_1\) and \(\mach_2\) in the induced trace from
    \(\mpstate{\mach_0}{\pinit(\callmap,\retmap,\mach_0)}\), if \(\own(\mach_1)
    \not = \own(\mach_2)\), then either \(\callmap(\mach_1) = n\) for some
    \(n\), or \(\retmap(\mach_1)\).

  \definition{Bracketing}

    A system enjoys {\em bracketing} with regard to a call map \(\callmap\) and
    a return map \(\retmap\) if for any initial state \(\mach_0\) and any
    call state and policy state \(\mach_c\) and \(\pol_c\) in the induced trace
    from \(\mpstate{\mach_0}{\pinit(\callmap,\retmap,\mach_0)}\), if
    \(\mpstate{\mach_c}{\pol_c} \hookrightarrow_P \MPT \mpostate{\mach'}
    {\pol'}{\obs'} | \retmap\) and \(\mpstate{\mach'}{\pol'} \stepstoobs{\obs'}
    \mpstate{\mach_r}{\pol_r}\), then \(\ret{\mach_c,\mach_r}\).

  \definition{Well-bracketed Control Flow}

    A system that enjoys control separation and bracketing with regard to some
    call map, return map, and ownership function enjoys {\em well-bracketed
    control flow} with respect to the three.
